Sleep, relative to wake, increases both veridical and false memory in the DRM paradigm: A registered report

### 2023-07-09 manuscript.Rmd
Added appendices

packagelist <- c('bookdown','knitr','markdown','osfr','plyr','tidyr','dplyr','emmeans','ggplot2','Rmisc','buildmer','lme4','lmerTest','stringr','effects','effectsize','ggdist','car','gridExtra','kableExtra','rstatix','LSAfun')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

Payne et al. [-@payne2009a] found that participants falsely recalled more critical lures post-sleep (vs. post-wake). However, it is possible that participants simply had a greater tendency to put down more unseen words after sleep, not because sleep increases DRM false recall per se. Therefore, before addressing our key research questions, we checked if participants across groups were comparable in terms of their bias in producing unseen items. In Payne et al. [-@payne2009a], this bias was indexed via the number of intrusions (i.e., neither the studied nor the lure items), which was roughly equivalent between their Sleep and Wake groups [MSleep = 5.6 vs. MWake = 6.2; p = .60] as well as between their AM and PM-control groups [MAM = 4.1 vs. MPM = 4.1; p = .99]. To check if this is the case in our data, we used a 2 (Interval: Immediate vs. Delay) $\times$ 2 (Test Time: AM vs. PM) Poisson regression. We chose Poisson regression, as opposed to ANOVA, because the intrusion data were count data, meaning that data distribution were right-skewed and hence unsuitable for ANOVA. Figure \@ref(fig:intrusionfig) summarises the number of intrusions in each group.

@@

>>>>

packagelist <- c('bookdown','knitr','markdown','osfr','plyr','tidyr','dplyr','emmeans','ggplot2','Rmisc','buildmer','lme4','lmerTest','stringr','effects','effectsize','ggdist','car','gridExtra','kableExtra','rstatix','LSAfun','simr')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

Payne et al. [-@payne2009a] found that participants falsely recalled more critical lures post-sleep (vs. post-wake). However, it is possible that participants simply had a greater tendency to put down more unseen words after sleep, not because sleep increases DRM false recall per se. Therefore, before addressing our key research questions, we checked if participants across groups were comparable in terms of their bias in producing unseen items. In Payne et al. [-@payne2009a], this bias was indexed via the number of intrusions (i.e., neither the studied nor the lure items), which was roughly equivalent between their Sleep and Wake groups [M$_{Sleep}$ = 5.6 vs. M$_{Wake}$ = 6.2; p = .60] as well as between their AM and PM-control groups [MAM = 4.1 vs. MPM = 4.1; p = .99]. To check if this is the case in our data, we used a 2 (Interval: Immediate vs. Delay) $\times$ 2 (Test Time: AM vs. PM) Poisson regression. We chose Poisson regression, as opposed to ANOVA, because the intrusion data were count data, meaning that data distribution were right-skewed and hence unsuitable for ANOVA. Figure \@ref(fig:intrusionfig) summarises the number of intrusions in each group.

@@

<div id="refs"></div>

# Appendix A: Screening Survey {.unnumbered}

# Appendix B: Survey in the test phase {.unnumbered}

# Appendix C: Justifications for using GLMM for false recall (as opposed to t-test/ANOVA) {.unnumbered}

The number of critical lures falsely recalled by a participant is count data, ranging from 0 to anything from 8 to 20 (depending on how many DRM lists were shown). In Payne et al. [-@payne2009a] for instance, the mean number of lure recalls was ~3.25 (out of 8). Count data with a low mean almost never approximates a normal distribution, because it is truncated at 0 (i.e., negative scores are impossible) and is skewed to the right [@herbison-a]. Parametric tests like t-test and ANOVA assume a normal distribution, so they are unlikely to be suitable for false recall data. GLMM, on the other hand, does not assume normal distribution [@lo2015a]. In addition, GLMM has numerous advantages over a t-test or an ANOVA; for instance, it can take by-participant and by-item variance into account, giving researchers the ability to test whether the effect of an independent variable generalises across participants and items [e.g., @brysbaert2018a].

# Appendix D: Power analysis {.unnumbered}

According to Newbury and Monaghan’s [-@newbury2019a] meta-analysis, the effect size for sleep in DRM false memory is Hedge’s g = +0.92 (95% CI: 0.54, 1.30; p < .001) in short lists (10 words per list).\footnote{Hedge’s g and Cohen’s d are interchangeable when the sample size is larger than 30 (Kline, 2004; Lakens, 2013).} However, due to certain biases in the psychology literature (e.g., publication bias), it has been argued that published effect sizes are generally inflated [e.g., @schaefer2019a] and that power analysis should be based on the lowest meaningful estimate [@albers2018a; @cortex2013a]. Therefore, we opted for a more conservative (yet contextualised) effect size estimate and went for the lower-bound of the 95% confidence interval reported by Newbury and Monaghan [-@newbury2019a], which is g = +0.54.

On estimating power in GLMM, a recent guideline [@kumle2021a] recommends using well-powered data from previous experiments. However, as far as we are aware, no prior ‘Sleep $\times$ DRM’ studies have made their data publicly available. We, therefore, simulated a dataset for our power calculation (available on OSF).

The first step is to determine a sample size. We have the financial resources to reach up to 160 participants/group (i.e., 640 in total), so we began by fabricating a dataset containing 120 participants/group. We made up 20 false recall observations for each participant. We then split the dataset by Interval, so one dataset for the Delay (Sleep + Wake) groups, another for the Immediate (AM + PM-control) groups, with each containing 4800 observations from 240 participants. In the first dataset, we simulated the false recall data for the Delay groups such that they approximated the data distribution [M$_{Sleep}$ = 45.9% (SD = 20.6%) vs M$_{Wake}$ = 36.3% (SD = 21.2%), p = .005] from a prior study (Payne et al., [-@payne2009a]; Experiment 1). Then, the data were manipulated to fit with our effect size assumption, such that the effect size for sleep is d = +0.54 [M$_{Sleep}$ = 44.7% (SD = 12.6%) vs. M$_{Wake}$ = 38.0% (SD = 12.0%); t(237.4) = 4.20, p = .001]. Afterwards, we simulated the false recall data in the second dataset for the AM and PM-control groups such that they also approximated the data distribution in Payne et al. [-@payne2009a] (Experiment 1; MAM = 42.5% (SD = 19.6%) vs. MPM = 46.3% (SD = 23.5%), p = .57) and that they did not differ significantly from each other [MAM = 42.9% (SD = 13.0%) vs. MPM= 43.5% (SD = 14%); t(233.3) = -0.37, p = .709, d = -0.05].\footnote{Notably, the standard deviations (SDs) from Payne et al. (2009; Experiment 1) are larger than those in our fabricated datasets. This is because Payne et al. showed only 8 wordlists (i.e., maximum lure recall = 8) while ours will show 20 (i.e., maximum lure recall = 20). To explain why this matters, a more concrete example here is useful: In Payne et al, a participant falsely recalling 3 lures would have a false recall rate of 37.5\% while another recalling 4 lures would have a rate of 50\%. So there is a 12.5\% difference between each successive number. In our fabricated data, recalling 3 lures has a false recall rate of 15\% while 4 lures has a rate of 20\%, so there is a 5\% difference. Therefore, understandably, the SDs in our fabricated datasets are necessarily lower than theirs (by roughly a half).}

We then merged the two fabricated datasets together and fitted a GLMM to it, using the lme4 package [@bates2015a]. The dependent variable, fixed effects structure, coding scheme, and computation procedures were identical to those described in section 12.3. Table D1 shows the fixed-effects estimates from the converged model, which has a by-participant intercept only.

Table D1

Based on the fixed-effects estimates, we estimated the power a sample size of 480 (i.e., 120/group) has for detecting an Interval and Test Time interaction. We conducted Monte Carlo simulation using the “simr” package [@green2016a] in R (see Box 2 for R codes). After 500 simulations, it was estimated that a sample of this size gives 90.1% power (95% CI: 87.03, 92.49) to detect a significant interaction. Then, we estimated the power we have for detecting a simple effect of Test Time within the Delay groups (i.e., Sleep vs. Wake). Following the simulation procedures above, it was estimated that 120 participants/group (i.e., 240 in the Delay groups) will give about 98.8% power (95% CI: 97.41, 99.56). In sum, our power calculation showed that having 120 participants/groups will give ample power (>90%) to detect both an Interval x Test Time interaction and a simple effect of Sleep vs. Wake. Finally, we also estimated that we will have at least 80% power as long as we have >99 participants/group. Therefore, in case we fail to reach our target sample size of 120 participants/group before funding expires but manage to recruit >99/group, our proposed experiment will still have satisfactory power.

We note that the focus of our proposed experiment is Research Question #1 [Does sleep (vs. wakefulness) influence DRM false recall?], so we based our power analysis on this question. Despite this, the estimate of 120 participants/group will also give over 90% power to detect the desired effects for Research Question #2 [Does sleep (vs. wake) increase veridical recall?], assuming the effect size for sleep is similar between Questions #1 and #2. Furthermore, since there are more studied list words than critical lures (160 vs. 20), the GLMM for addressing Question #2 will have substantially more observations than that for Question #1 (~76800 vs. ~9600), boosting power on the item level. In short, our target sample size of 120 participants/group will give us sufficient power for both Research Questions.

## Box 2 {.unnumbered}

*R codes for Monte Carlo simulation*

```{r box2, include=TRUE, eval=FALSE, echo=TRUE}

library(simr)
fixef(fabricated_model)["Interval1:Test_Time1"] <- 0.076
set.seed(99)
powerSim(fabricated_model, fixed("Interval1:Test_Time1"), nsim=500)

### 2023-07-09 manuscript.tex
Added appendices

Payne et al. {[}\protect\hyperlink{ref-payne2009a}{6}{]} found that participants falsely recalled more critical lures post-sleep (vs.~post-wake). However, it is possible that participants simply had a greater tendency to put down more unseen words after sleep, not because sleep increases DRM false recall per se. Therefore, before addressing our key research questions, we checked if participants across groups were comparable in terms of their bias in producing unseen items. In Payne et al. {[}\protect\hyperlink{ref-payne2009a}{6}{]}, this bias was indexed via the number of intrusions (i.e., neither the studied nor the lure items), which was roughly equivalent between their Sleep and Wake groups {[}MSleep = 5.6 vs.~MWake = 6.2; p = .60{]} as well as between their AM and PM-control groups {[}MAM = 4.1 vs.~MPM = 4.1; p = .99{]}. To check if this is the case in our data, we used a 2 (Interval: Immediate vs.~Delay) \(\times\) 2 (Test Time: AM vs.~PM) Poisson regression. We chose Poisson regression, as opposed to ANOVA, because the intrusion data were count data, meaning that data distribution were right-skewed and hence unsuitable for ANOVA. Figure \ref{fig:intrusionfig} summarises the number of intrusions in each group.

@@

@@

>>>>

Payne et al. {[}\protect\hyperlink{ref-payne2009a}{6}{]} found that participants falsely recalled more critical lures post-sleep (vs.~post-wake). However, it is possible that participants simply had a greater tendency to put down more unseen words after sleep, not because sleep increases DRM false recall per se. Therefore, before addressing our key research questions, we checked if participants across groups were comparable in terms of their bias in producing unseen items. In Payne et al. {[}\protect\hyperlink{ref-payne2009a}{6}{]}, this bias was indexed via the number of intrusions (i.e., neither the studied nor the lure items), which was roughly equivalent between their Sleep and Wake groups {[}M\(_{Sleep}\) = 5.6 vs.~M\(_{Wake}\) = 6.2; p = .60{]} as well as between their AM and PM-control groups {[}MAM = 4.1 vs.~MPM = 4.1; p = .99{]}. To check if this is the case in our data, we used a 2 (Interval: Immediate vs.~Delay) \(\times\) 2 (Test Time: AM vs.~PM) Poisson regression. We chose Poisson regression, as opposed to ANOVA, because the intrusion data were count data, meaning that data distribution were right-skewed and hence unsuitable for ANOVA. Figure \ref{fig:intrusionfig} summarises the number of intrusions in each group.

@@

\leavevmode\vadjust pre{\hypertarget{ref-herbison-a}{}}%
\CSLLeftMargin{38. }%
\CSLRightInline{Herbison P. n.d.\href{https://www.ics.org/Abstracts/Publish/44/000161.pdf}{Analysing count data}. }

\leavevmode\vadjust pre{\hypertarget{ref-lo2015a}{}}%
\CSLLeftMargin{39. }%
\CSLRightInline{Lo S, Andrews S. 2015 To transform or not to transform: Using generalized linear mixed models to analyse reaction time data. \emph{Frontiers in Psychology} \textbf{6}, 1171. (doi:\href{https://doi.org/10.3389/fpsyg.2015.01171}{10.3389/fpsyg.2015.01171})}

\leavevmode\vadjust pre{\hypertarget{ref-brysbaert2018a}{}}%
\CSLLeftMargin{40. }%
\CSLRightInline{Brysbaert M, Stevens M. 2018 Power analysis and effect size in mixed effects models: A tutorial. \emph{Journal of Cognition} \textbf{1}, 1--20. (doi:\href{https://doi.org/10.5334/joc.10}{10.5334/joc.10})}

\leavevmode\vadjust pre{\hypertarget{ref-schaefer2019a}{}}%
\CSLLeftMargin{41. }%
\CSLRightInline{Schäfer T, Schwarz MA. 2019 The meaningfulness of effect sizes in psychological research: Differences between sub-disciplines and the impact of potential biases. \emph{Frontiers in Psychology} \textbf{10}, 1--13. (doi:\href{https://doi.org/10.3389/fpsyg.2019.00813}{10.3389/fpsyg.2019.00813})}

\leavevmode\vadjust pre{\hypertarget{ref-albers2018a}{}}%
\CSLLeftMargin{42. }%
\CSLRightInline{Albers C, Lakens D. 2018 When power analyses based on pilot data are biased: Inaccurate effect size estimators and follow-up bias. \emph{Journal of experimental social psychology} \textbf{74}, 187--195. (doi:\href{https://doi.org/10.1016/j.jesp.2017.09.004}{10.1016/j.jesp.2017.09.004})}

\leavevmode\vadjust pre{\hypertarget{ref-cortex2013a}{}}%
\CSLLeftMargin{43. }%
\CSLRightInline{Cortex. 2013 \href{https://www.elsevier.com/__data/promis_misc/PROMIS\%20pub_idt_CORTEX\%20Guidelines_RR_29_04_2013.pdf}{Guidelines for authors}. }

\leavevmode\vadjust pre{\hypertarget{ref-kumle2021a}{}}%
\CSLLeftMargin{44. }%
\CSLRightInline{Kumle L, Võ MLH, Draschkow D. 2021 Estimating power in (generalized) linear mixed models: An open introduction and tutorial in r. \emph{Behavior research methods} \textbf{53}, 2528--2543. (doi:\href{https://doi.org/10.3758/s13428-021-01546-0}{10.3758/s13428-021-01546-0})}

\leavevmode\vadjust pre{\hypertarget{ref-bates2015a}{}}%
\CSLLeftMargin{45. }%
\CSLRightInline{Bates D, Kliegl R, Vasishth S, Baayen H. 2015 Parsimonious mixed models. }

\leavevmode\vadjust pre{\hypertarget{ref-green2016a}{}}%
\CSLLeftMargin{46. }%
\CSLRightInline{Green P, Macleod CJ. 2016 SIMR: An r package for power analysis of generalized linear mixed models by simulation. \emph{Methods in Ecology and Evolution} \textbf{7}, 493--498. (doi:\href{https://doi.org/10.1111/2041-210X.12504}{10.1111/2041-210X.12504})}

@@

\hypertarget{appendix-a-screening-survey}{%
\section*{Appendix A: Screening Survey}\label{appendix-a-screening-survey}}
\addcontentsline{toc}{section}{Appendix A: Screening Survey}

\hypertarget{appendix-b-survey-in-the-test-phase}{%
\section*{Appendix B: Survey in the test phase}\label{appendix-b-survey-in-the-test-phase}}
\addcontentsline{toc}{section}{Appendix B: Survey in the test phase}

\hypertarget{appendix-c-justifications-for-using-glmm-for-false-recall-as-opposed-to-t-testanova}{%
\section*{Appendix C: Justifications for using GLMM for false recall (as opposed to t-test/ANOVA)}\label{appendix-c-justifications-for-using-glmm-for-false-recall-as-opposed-to-t-testanova}}
\addcontentsline{toc}{section}{Appendix C: Justifications for using GLMM for false recall (as opposed to t-test/ANOVA)}

The number of critical lures falsely recalled by a participant is count data, ranging from 0 to anything from 8 to 20 (depending on how many DRM lists were shown). In Payne et al. {[}\protect\hyperlink{ref-payne2009a}{6}{]} for instance, the mean number of lure recalls was \textasciitilde3.25 (out of 8). Count data with a low mean almost never approximates a normal distribution, because it is truncated at 0 (i.e., negative scores are impossible) and is skewed to the right {[}\protect\hyperlink{ref-herbison-a}{38}{]}. Parametric tests like t-test and ANOVA assume a normal distribution, so they are unlikely to be suitable for false recall data. GLMM, on the other hand, does not assume normal distribution {[}\protect\hyperlink{ref-lo2015a}{39}{]}. In addition, GLMM has numerous advantages over a t-test or an ANOVA; for instance, it can take by-participant and by-item variance into account, giving researchers the ability to test whether the effect of an independent variable generalises across participants and items {[}e.g., \protect\hyperlink{ref-brysbaert2018a}{40}{]}.

\hypertarget{appendix-d-power-analysis}{%
\section*{Appendix D: Power analysis}\label{appendix-d-power-analysis}}
\addcontentsline{toc}{section}{Appendix D: Power analysis}

According to Newbury and Monaghan's {[}\protect\hyperlink{ref-newbury2019a}{1}{]} meta-analysis, the effect size for sleep in DRM false memory is Hedge's g = +0.92 (95\% CI: 0.54, 1.30; p \textless{} .001) in short lists (10 words per list).\footnote{Hedge’s g and Cohen’s d are interchangeable when the sample size is larger than 30 (Kline, 2004; Lakens, 2013).} However, due to certain biases in the psychology literature (e.g., publication bias), it has been argued that published effect sizes are generally inflated {[}e.g., \protect\hyperlink{ref-schaefer2019a}{41}{]} and that power analysis should be based on the lowest meaningful estimate {[}\protect\hyperlink{ref-albers2018a}{42},\protect\hyperlink{ref-cortex2013a}{43}{]}. Therefore, we opted for a more conservative (yet contextualised) effect size estimate and went for the lower-bound of the 95\% confidence interval reported by Newbury and Monaghan {[}\protect\hyperlink{ref-newbury2019a}{1}{]}, which is g = +0.54.

On estimating power in GLMM, a recent guideline {[}\protect\hyperlink{ref-kumle2021a}{44}{]} recommends using well-powered data from previous experiments. However, as far as we are aware, no prior `Sleep \(\times\) DRM' studies have made their data publicly available. We, therefore, simulated a dataset for our power calculation (available on OSF).

The first step is to determine a sample size. We have the financial resources to reach up to 160 participants/group (i.e., 640 in total), so we began by fabricating a dataset containing 120 participants/group. We made up 20 false recall observations for each participant. We then split the dataset by Interval, so one dataset for the Delay (Sleep + Wake) groups, another for the Immediate (AM + PM-control) groups, with each containing 4800 observations from 240 participants. In the first dataset, we simulated the false recall data for the Delay groups such that they approximated the data distribution {[}M\(_{Sleep}\) = 45.9\% (SD = 20.6\%) vs M\(_{Wake}\) = 36.3\% (SD = 21.2\%), p = .005{]} from a prior study (Payne et al., {[}\protect\hyperlink{ref-payne2009a}{6}{]}; Experiment 1). Then, the data were manipulated to fit with our effect size assumption, such that the effect size for sleep is d = +0.54 {[}M\(_{Sleep}\) = 44.7\% (SD = 12.6\%) vs.~M\(_{Wake}\) = 38.0\% (SD = 12.0\%); t(237.4) = 4.20, p = .001{]}. Afterwards, we simulated the false recall data in the second dataset for the AM and PM-control groups such that they also approximated the data distribution in Payne et al. {[}\protect\hyperlink{ref-payne2009a}{6}{]} (Experiment 1; MAM = 42.5\% (SD = 19.6\%) vs.~MPM = 46.3\% (SD = 23.5\%), p = .57) and that they did not differ significantly from each other {[}MAM = 42.9\% (SD = 13.0\%) vs.~MPM= 43.5\% (SD = 14\%); t(233.3) = -0.37, p = .709, d = -0.05{]}.\footnote{Notably, the standard deviations (SDs) from Payne et al. (2009; Experiment 1) are larger than those in our fabricated datasets. This is because Payne et al. showed only 8 wordlists (i.e., maximum lure recall = 8) while ours will show 20 (i.e., maximum lure recall = 20). To explain why this matters, a more concrete example here is useful: In Payne et al, a participant falsely recalling 3 lures would have a false recall rate of 37.5\% while another recalling 4 lures would have a rate of 50\%. So there is a 12.5\% difference between each successive number. In our fabricated data, recalling 3 lures has a false recall rate of 15\% while 4 lures has a rate of 20\%, so there is a 5\% difference. Therefore, understandably, the SDs in our fabricated datasets are necessarily lower than theirs (by roughly a half).}

We then merged the two fabricated datasets together and fitted a GLMM to it, using the lme4 package {[}\protect\hyperlink{ref-bates2015a}{45}{]}. The dependent variable, fixed effects structure, coding scheme, and computation procedures were identical to those described in section 12.3. Table D1 shows the fixed-effects estimates from the converged model, which has a by-participant intercept only.

Table D1

Based on the fixed-effects estimates, we estimated the power a sample size of 480 (i.e., 120/group) has for detecting an Interval and Test Time interaction. We conducted Monte Carlo simulation using the ``simr'' package {[}\protect\hyperlink{ref-green2016a}{46}{]} in R (see Box 2 for R codes). After 500 simulations, it was estimated that a sample of this size gives 90.1\% power (95\% CI: 87.03, 92.49) to detect a significant interaction. Then, we estimated the power we have for detecting a simple effect of Test Time within the Delay groups (i.e., Sleep vs.~Wake). Following the simulation procedures above, it was estimated that 120 participants/group (i.e., 240 in the Delay groups) will give about 98.8\% power (95\% CI: 97.41, 99.56). In sum, our power calculation showed that having 120 participants/groups will give ample power (\textgreater90\%) to detect both an Interval x Test Time interaction and a simple effect of Sleep vs.~Wake. Finally, we also estimated that we will have at least 80\% power as long as we have \textgreater99 participants/group. Therefore, in case we fail to reach our target sample size of 120 participants/group before funding expires but manage to recruit \textgreater99/group, our proposed experiment will still have satisfactory power.

We note that the focus of our proposed experiment is Research Question \#1 {[}Does sleep (vs.~wakefulness) influence DRM false recall?{]}, so we based our power analysis on this question. Despite this, the estimate of 120 participants/group will also give over 90\% power to detect the desired effects for Research Question \#2 {[}Does sleep (vs.~wake) increase veridical recall?{]}, assuming the effect size for sleep is similar between Questions \#1 and \#2. Furthermore, since there are more studied list words than critical lures (160 vs.~20), the GLMM for addressing Question \#2 will have substantially more observations than that for Question \#1 (\textasciitilde76800 vs.~\textasciitilde9600), boosting power on the item level. In short, our target sample size of 120 participants/group will give us sufficient power for both Research Questions.

\hypertarget{box-2}{%
\subsection*{Box 2}\label{box-2}}
\addcontentsline{toc}{subsection}{Box 2}

\emph{R codes for Monte Carlo simulation}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(simr)}
\FunctionTok{fixef}\NormalTok{(fabricated\_model)[}\StringTok{"Interval1:Test\_Time1"}\NormalTok{] }\OtherTok{\textless{}{-}} \FloatTok{0.076}
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{99}\NormalTok{)}
\FunctionTok{powerSim}\NormalTok{(fabricated\_model, }\FunctionTok{fixed}\NormalTok{(}\StringTok{"Interval1:Test\_Time1"}\NormalTok{), }\AttributeTok{nsim=}\DecValTok{500}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
